Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-05-11 Thesis/chapter/03-theoretical-background.tex
400 words sputtering freewriting

\subsection{Sputtering}
% https://en.wikipedia.org/wiki/Sputter_deposition
\td{what is the principle behind sputtering
what is sputtering, how does it work, what different kinds of sputtering is there, 
what is is used for? 
what was it used for in this work? 
}
\td{
- phenomon of high energy particle bombardement know off particles from a source\\
- options to create high energy particles: electron gun, thermal evaporation or cathode? 
- vorteile sind: Swann p 67(2)
- need low pressure bcs of MFP but plasma needs gas to sustain
- source is target and target is substrate

}
%Sputtering is a physical deposition method. 
Sputtering describes the process of particles being sputtered from a surface after 
impact of highly energetic particles.
These high energy particles start cascades of momentum transfers. 
If a path of a cascade reaches back to the surface and the kinetic energy of a surface 
particle exceeds the binding energy, it is ejected (or sputtered).

%Sputtering describes the process when highly energetic particles collide with a surface 
%and through a cascade of momentum transfers surface particles are depleted and sputter from the surface.
This process occurs naturally in outer space (through alpha particles, electrons etc.) 
and is used in science and technology for 
sputter cleaning, thin film deposition, analysis or etching. 
The phenomenon was discovered and identified as an atomic collision phenomenon in the 
middle of the 20th century and now is a field of research with its own niche subfields 
(e.g. sputtering of exotic materials (such as condensed gases, planetary
atmospheres, lunar dust grains, proteins and viruses), high density cascades and 
linear cascades, which could be called classical sputtering)
%sputtering of insulators and biomolecular material)
\cite{Sigmund1987}.
%
In this work it was used to deposit thin gold contacts through a mask. 
A directional current sputtering machine was used. 
\td{describe the machine}
A argon plasma in a strong electrical field (some kV) provides the highly energetic particles. 
Argon ions are accelerated through the field to the source (a metal wafer), which acts as cathode, and start cascades. 
In order to maximise the yield (sputtering speed) a magnet is used to trap the plasma close to source. 
Plasma sputtering with a strong magnet to 
1.5h 
\\
\td{A high voltage is angelegt at the source (a metal wafer). 
Electrons with a high kinetic energy bump into the source and herausschießen metal atoms, 
which will deposit on a target. 
By ausrüsten the target with a mask, arbitrary musters can be obtained (e.g. contact arrays).
}
How are the electrons erzeugt? 
\td{With a magnetron (a micro wave erzeuging high vacuum bauteil) a plasma is sustained. 
}
Find source

>>>>

\subsection{Sputtering}
% https://en.wikipedia.org/wiki/Sputter_deposition
\td{what is the principle behind sputtering
what is sputtering, how does it work, what different kinds of sputtering is there, 
what is is used for? 
what was it used for in this work? 
}
\td{
- phenomon of high energy particle bombardement know off particles from a source
- options to create high energy particles: electron gun, thermal evaporation or cathode? 
- vorteile sind: Swann p 67(2)
- need low pressure bcs of MFP but plasma needs gas to sustain
- source is target and target is substrate
}
%Sputtering is a physical deposition method. 
Sputtering describes the process of particles being sputtered from a surface after 
impact of highly energetic particles.
These high energy particles start cascades of momentum transfers. 
If a path of a cascade reaches back to the surface and the kinetic energy of a surface 
particle exceeds the binding energy, it is ejected (or sputtered).

%Sputtering describes the process when highly energetic particles collide with a surface 
%and through a cascade of momentum transfers surface particles are depleted and sputter from the surface.
This process occurs naturally in outer space (through alpha particles, electrons etc.) 
and is used in science and technology for 
sputter cleaning, thin film deposition, analysis or etching. 
The phenomenon was discovered and identified as an atomic collision phenomenon in the 
middle of the 20th century and now is a field of research with its own niche subfields 
(e.g. sputtering of exotic materials (such as condensed gases, planetary
atmospheres, lunar dust grains, proteins and viruses), high density cascades and 
linear cascades, which could be called classical sputtering)
%sputtering of insulators and biomolecular material)
\cite{Sigmund1987}.
%
In this work it was used to deposit thin gold contacts through a mask. 
A directional current sputtering machine was used. 
\td{describe the machine}
A argon plasma in a strong electrical field (some kV) provides the highly energetic particles. 
Argon ions are accelerated through the field to the source (a metal wafer), which acts as cathode, and start cascades. 
In order to maximise the yield (sputtering speed) a magnet is used to trap the plasma close to source. 
Plasma sputtering with a strong magnet to 
1.5h 
\\
\td{A high voltage is angelegt at the source (a metal wafer). 
Electrons with a high kinetic energy bump into the source and herausschießen metal atoms, 
which will deposit on a target. 
By ausrüsten the target with a mask, arbitrary musters can be obtained (e.g. contact arrays).
}
How are the electrons erzeugt? 
\td{With a magnetron (a micro wave erzeuging high vacuum bauteil) a plasma is sustained. 
}
Find source\\\\

SPUTTERING FREEWRITING: 
what is sputtering? \\
sputtering is the processes of highly energetic ions (only ions?) hitting a surface and atoms or molecules being expelled. 
This is a physical vapor deposition technique (PVD). PVD can be unterteils in thermal and highly energetic activated. Sputtering is part of HEA, which hast the convenience, that some substrates don't withstand high temperatures. 
what can it be used for?\\
Sputtering moved from being a curious experiment to having multi anwendungen in science (forschung) and engineering, becuase the sputtered materials can be deposited on  substrate. 
anwendungen reichen from, thin films for PV, electrical circuits, storage media such as CDs and DVDs etc. 
Vorteile of sputtering are also a good adherent to the substrate and good step coverage and what else? 
different styles\\
The most successful durchgesetzte kind of sputtering devices are magnetron sputtering devices, which wiederum can be unterteilt in DC (directional current) RF (radio frequency) sputtering and reactive sputtering. 
how does it work? \\
A high voltage is applied to the source (make skizze), which acts as a cathode. 
The cathode, then, emits electrons which collide with XXX gas (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
The argon may get ionized by electron and the argon cation will be accelerated to the cathode. If the cation has enough energy it will bump off a target atom or molecule. 
This happens by a cascade of momentum transfers, which can reach the surface again. 
If the suface particle gets momentum pointing from the surface and the remaining kinetic energy is higher then the binding energy, the particle is sputtered. 
The pressure should be small, such that the sputtered particle has a moeglichst long mean free path (MFP), but on the other hand there is a minimum pressure to keep the plasma going. 
Usual pressures are around (1 mPa?).
\td{mention the substrate parallel to the target}

A magnetron can be placed behind the cathode (target) in order to trap ejected ions close to the electron source. 
This prevents high energy electrons from reaching the target and undoing the deposited layer and increasing the probability of an electron colliding with an argon atom and ionizing it
